Concurrent, Parallel Garbage Collection in Linear Time

### 2016-06-01 finaletd/mainintroduction.tex
changes

\paragraph{Locality based garbage collection:}
Detecting garbage is a global predicate. Traditionally, popular methods of garbage collection algorithm involve computing garbage as the global predicate. This requires scanning entire heap for precise evaluation of the predicate. If garbage object can be detected locally based on the small set of object, then the garbage detection process can save a lot of time spent on tracing all objects in the heap.

@@

In a shared memory system, the conventional single-threaded garbage collector does not scale well with an increase in the size of memory and number of processor. A locality based concurrent multi-collector garbage collector is hope for achieving scalability in shared memory systems.

@@

>>>>

\paragraph{Locality-based garbage collection:}
Detecting garbage is a global predicate. Traditionally, popular methods of garbage collection involve computing garbage as the global predicate. This requires scanning the entire heap for precise evaluation of the predicate. If garbage object can be detected locally based on the small set of objects, then the garbage detection process can save a lot of time spent by not tracing all objects in the heap.

@@

Shared memory and distributed memory systems does not have a scalable garbage collectors up until now. In shared memory systems, scalability is an issue due to most collectors designed are primarily single collector concurrent algorithm. In distributed system, all available garbage collectors require a form of global synchronization to detect garbage. To meet future demands of scalable garbage collection, collectors must be multi-collector locality-based with no global synchronization.
\begin{comment}
In a shared memory system, the conventional single-threaded garbage collector does not scale well with an increase in the size of memory and number of processors. A locality-based concurrent multi-collector garbage collector is best possible solution for achieving scalability in shared memory systems.

@@

\end{comment}
